Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-06-16 thirdPaper/draft/typeConeAssociahedra.tex
minor change

The following statement describes the type cone of the non-kissing fan of a brick and $2$-acyclic gentle quiver.
We provide here an elementary combinatorial proof, a deeper and more general reason is discussed in \cref{coro::simplicialTypeConeNKCalgebraic}.

@@

>>>>

The following statement describes the type cone of the non-kissing fan of a brick and $2$-acyclic gentle quiver.
We provide here an elementary combinatorial proof, a more general representation theoretic perspective is discussed in \cref{theo::brick-algebra-condition}.

@@

Our next statement follows from the end of the previous proof.
See also \cref{coro::simplicialTypeConeNKCalgebraic}.
